Tropical Andes plant Lookup Table

### 2023-09-12 code/L1/L1_TropicalAndes_plant_lookupTable.Rmd
split gbif calls up even more seperate code chunks

```{r}
#split up gbif species list to speed up api call
GBIF_species1 <-GBIF_species[1:33107,]
GBIF_species2 <-GBIF_species[33107:66214,]
GBIF_species3 <-GBIF_species[66214:99321,]
GBIF_species4 <-GBIF_species[99321:132428,]

GBIF_results1 <- TNRS(taxonomic_names = GBIF_species1)
GBIF_results2 <- TNRS(taxonomic_names = GBIF_species2)
GBIF_results3 <- TNRS(taxonomic_names = GBIF_species3)
GBIF_results4 <- TNRS(taxonomic_names = GBIF_species4)
```

```{r}
#combine gbif results
GBIF_results <- rbind(GBIF_results1, GBIF_results2, GBIF_results3, GBIF_results4)
```

>>>>

```{r}
#split up gbif species list to speed up api call
GBIF_species1 <-GBIF_species[1:16553,]
GBIF_species2 <-GBIF_species[16553:33107,]
GBIF_species3 <-GBIF_species[33107:49660,]
GBIF_species4 <-GBIF_species[49660:66214,]
GBIF_species5 <-GBIF_species[66214:82767,]
GBIF_species6 <-GBIF_species[82767:99321,]
GBIF_species7 <-GBIF_species[99321:115874,]
GBIF_species8 <-GBIF_species[115874:132428,]
```

```{r}
#run one line at a time for best results
GBIF_results1 <- TNRS(taxonomic_names = GBIF_species1)
GBIF_results2 <- TNRS(taxonomic_names = GBIF_species2)
GBIF_results3 <- TNRS(taxonomic_names = GBIF_species3)
GBIF_results4 <- TNRS(taxonomic_names = GBIF_species4)
GBIF_results5 <- TNRS(taxonomic_names = GBIF_species5)
GBIF_results6 <- TNRS(taxonomic_names = GBIF_species6)
GBIF_results7 <- TNRS(taxonomic_names = GBIF_species7)
GBIF_results8 <- TNRS(taxonomic_names = GBIF_species8)
```

```{r}
#combine gbif results
GBIF_results <- rbind(GBIF_results1, GBIF_results2, GBIF_results3, GBIF_results4, GBIF_results5, GBIF_results6, GBIF_results7, GBIF_results8)
```
